\documentclass{article}
\usepackage{graphicx} 
\usepackage{amsmath}
\usepackage{hyperref}

\title{Project Milestone 1}
\author{
K. Anjuli Jones (anjulij) 
Matthew Dam (3clipseS)
\\Daniel De Oliveira (danherbb)
\\Carlos Vasquez
}
\date{15 February 2026}

\begin{document}

\maketitle

\section*{Project}
GitHub Repository \href{https://github.com/anjulij/COP4533-Final-Project}{Link}
\\Communication method: Discord
\\Member Roles: 
\\ \href{https://docs.google.com/spreadsheets/d/1yOdtYDnJk8dgZALbhoqwJsnvrXZ8V31M7DZmk_DKJYQ/edit?usp=sharing}{Project Gantt Chart}: (including internal deadlines and meetings)

\section*{Milestone 1: Understanding the Problem}
\subsection*{Problem 1}

\noindent \textbf{Step 1.} Input matrix A
$$A = 
\begin{bmatrix}
    12 & 1 & 5 & 3 & 16 \\
    4 & 4 & 13 & 4 & 9 \\
    6 & 8 & 6 & 1 & 2 \\
    14 & 3 & 4 & 8 & 10 \\
\end{bmatrix}
$$

\medskip
\noindent \textbf{Step 2.} Potential profit by selling on each day for each stock.

\medskip
Let $p_{i,j}$ be the potential profit of selling stock $i$ on day $j$. Then,
\begin{itemize}
	\item $p_{1,1} = 0$, $p_{1,2} = 0$, $p_{1,3} = 4$, $p_{1,4} = 2$, $p_{1,5} = 15$
	\item $p_{2,1} = 0$, $p_{2,2} = 0$, $p_{2,3} = 9$, $p_{2,4} = 0$, $p_{2,5} = 5$
	\item $p_{3,1} = 0$, $p_{3,2} = 2$, $p_{3,3} = 0$, $p_{3,4} = 0$, $p_{3,5} = 1$
	\item $p_{4,1} = 0$, $p_{4,2} = 0$, $p_{4,3} = 1$, $p_{4,4} = 5$, $p_{4,5} = 7$
\end{itemize}

\medskip
\noindent \textbf{Step 3.} Identify the day with the highest potential profit for each stock.

\medskip
Based on the calculated values for $p_{i,j}$ in the previous step,
\begin{itemize}
    \item $max_{j}p_{1,j} = 15$, on day $5$
    \item $max_{j}p_{2,j} = 9$, on day $3$
    \item $max_{j}p_{3,j} = 2$, on day $2$
    \item $max_{j}p_{4,j} = 7$, on day $5$
\end{itemize}

\medskip
\noindent \textbf{Step 4.} Determine the stock and day combination that yields the maximum potential profit.

\medskip
Based on step 3, the maximum potential profit is $15$ and is obtained by selling the first stock on the fifth day. The stock would be bought on the second day, therefore the output for this example would be
$$(1, 2, 5, 15)$$

\subsection*{Problem 2}
Work out the given numerical example for Problem-2. That is, You are given a matrix A of dimensions $ \times n$, where each element represents the predicted prices of m different stocks for n consecutive days. Additionally, you are given an integer $k (1 \leq k \leq n)$. Your task is to manually find a sequence of at most $k$ transactions, each involving the purchase and sale of a single stock, that yields the maximum profit. (Refer to problem statement - 2 for output format).

\paragraph{Input Matrix A}

\[
A =
\begin{bmatrix}
    25 & 30 & 15 & 40 & 50 \\
    10 & 20 & 30 & 25 & 5\\
    30 & 45 & 35 & 10 & 15\\
    5 & 50 & 35 & 25 & 45
\end{bmatrix}
\]
\[k = 3\]

\paragraph{Steps}
\begin{enumerate}
    \item  Begin with the input matrix A as provided.
    \item Determine the sequence of at-most K non-overlapping transactions. A valid transaction is a buy-sell of the same stock. Different transactions can have different stocks, but one transaction would deal with only a single stock.
    \item Output should be a sequence of at most K transactions in the format of $(i,j,l)$ that yields the maximum potential profit by selling ith stock on lth day that was bought on jth day.
\end{enumerate}

\subsubsection*{Notes}

\begin{itemize}
  \item This milestone involves manually applying the basic logic of calculating potential profits and selecting the optimal transaction for a single stock.
\item The goal is to understand the foundational logic of finding the maximum profit for atmost K non-overlapping transactions by considering the price differences between different days for a specific
stock (in a single transaction).
\end{itemize}

\subsection*{Problem 3}
\[
A =
\begin{bmatrix}
    7 & 1 & 5 & 3 & 6 & 8 & 9 \\
    2 & 4 & 3 & 7 & 9 & 1 & 8 \\
    5 & 8 & 9 & 1 & 2 & 3 & 10 \\
    9 & 3 & 4 & 8 & 7 & 4 & 1 \\
    3 & 1 & 5 & 8 & 9 & 6 & 4
\end{bmatrix}
\]
\[c = 2\]
\medskip
\noindent \textbf{Step 1.}  Begin with the input matrix A and integer c as provided

\medskip
\noindent \textbf{Step 2.} For each day $j$, identify the maximum price to sell the stock $\ell$. 
You can only buy another stock after $c + 1$ days (i.e., on day $\ell + c + 1$ or later).

\medskip
Let $i$ = stock number; $j$ = buy day; $\ell$ = sale day.

\medskip
\textbf{1 Buy 1 Sell Combinations}

\[
\begin{aligned}
(1,2,7) &:\quad profit = 8 \\
(2,6,7) &:\quad profit = 7 \\
(3,4,7) &:\quad profit = 9 \\
(4,2,4) &:\quad profit = 5 \\
(5,2,5) &:\quad profit = 8 \\
\vdots
\end{aligned}
\]

\medskip
\textbf{2 Buy 2 Sell Combinations}

\[
\begin{aligned}
(1,1,2), (1,5,7) &:\quad profit = -3 \\
(2,1,2), (2,6,7) &:\quad profit = 5 \\
(3,1,2), (3,5,7) &:\quad profit = 11 \\
(4,1,2), (4,6,7) &:\quad profit = -9 \\
(5,1,2), (5,6,7) &:\quad profit = -4 \\
\vdots
\end{aligned}
\]

\[
\begin{aligned}
(1,2,3), (1,6,7) &:\quad profit = 5 \\
(2,1,3), (2,6,7) &:\quad profit = 8 \\
(3,1,3), (3,6,7) &:\quad profit = 11 \\
(4,2,3), (4,6,7) &:\quad profit = -2 \\
(5,2,3), (5,6,7) &:\quad profit = 2 \\
\vdots
\end{aligned}
\]

\medskip
\noindent \textbf{Step 3.} Determine the sequence (i,j,l) that yields the maximum potential profit by selling ith stock on lth day that was bought on jth day.

\medskip
Maximum profit found is 11. Therefore, the sequences that yields the maximum potential profit are
\[
\left[(3,1,3),(3,6,7)\right]
\quad \text{and} \quad
\left[(3,1,2),(3,5,7)\right].
\]
\end{document}
